Nail: A practical interface generator for data formats

### 2014-05-02 paper/osdi14/abstract.tex
Fixed citations

\textit{Nail} is an tools that greatly reduces the
programmer effort for safely parsing and generating data formats defined
by a grammar.
Nail introduces several key
ideas to achieve its goal.  First, Nail uses the protocol grammar to
define not just the data format, but also the internal object model
of the data.  Second, Nail eliminates the notion of semantic actions,
used by existing parser generators, which reduces the expressive power
but allows Nail to both {\em parse} data formats and {\em generate}
them from the internal object model, by maintaining a {\em semantic
bijection} between the data format and the object model.  Third,
Nail introduces {\em dependency fields} and {\em stream transforms} to
capture protocol features such as size and offset fields, checksums,
and compressed data, which are impractical to express in existing
protocol languages.  Using Nail, we implement an authoritative  DNS server in
C in under 300 lines of code and grammar, and an {\tt unzip}
program in C in 220 lines of code and grammar, demonstrating that Nail
makes it easy to parse complex real-world data formats.  Performance
experiments show that a Nail-based DNS server can outperform the widely
used BIND DNS server, demonstrating that Nail parsers can achieve good
performance.

>>>>

\textit{Nail} is an tools that greatly reduces the
programmer effort for safely parsing and generating data formats defined
by a grammar.
Nail introduces several key
ideas to achieve its goal.  First, Nail uses the protocol grammar to
define not just the data format, but also the internal object model
of the data.  Second, Nail eliminates the notion of semantic actions,
used by existing parser generators, which reduces the expressive power
but allows Nail to both {\em parse} data formats and {\em generate}
them from the internal object model, by maintaining a {\em semantic
bijection} between the data format and the object model.  Third,
Nail introduces {\em dependent fields} and {\em stream transforms} to
capture protocol features such as size and offset fields, checksums,
and compressed data, which are impractical to express in existing
protocol languages.  Using Nail, we implement an authoritative  DNS server in
C in under 300 lines of code and grammar, and an {\tt unzip}
program in C in 220 lines of code and grammar, demonstrating that Nail
makes it easy to parse complex real-world data formats.  Performance
experiments show that a Nail-based DNS server can outperform the widely
used BIND DNS server, demonstrating that Nail parsers can achieve good
performance.

### 2014-05-02 paper/osdi14/eval.tex
Fixed citations

Duplicating information made sense when ZIP files were stored on floppy
disks with slow seek times and high fault rates, and memory constraints
made it impossible to keep the ZIP directory in memory or the archive
was split across multiple disks.  However, care must be taken that the
metadata is consistent. For example, vulnerabilities could occur if
the length in the central directory is used to allocate memory and the
length in the local directory is used to extract without checking that
they are equal first, as was the case in the Python ZIP
library~\cite{cve-python-zip-maybe}.

>>>>

Duplicating information made sense when ZIP files were stored on floppy
disks with slow seek times and high fault rates, and memory constraints
made it impossible to keep the ZIP directory in memory or the archive
was split across multiple disks.  However, care must be taken that the
metadata is consistent. For example, vulnerabilities could occur if
the length in the central directory is used to allocate memory and the
length in the local directory is used to extract without checking that
they are equal first, as was the case in the Python ZIP
library~\cite{cve-2012-7338}.

### 2014-05-02 paper/osdi14/intro.tex
Fixed citations

Second,  applications often need to produce output in the same
format as their input---for example, applications might both
read and write files, or both receive and send network packets.
Most parser generators focus on just parsing an input, rather
than producing an output, thus requiring the programmer to manually
construct outputs, which is error-prone.
\XXX[do we have any evidence to cite for this claim?]
Some parser generators, such as
Boost.Spirit~\cite{boost-spirit},
allow reusing the grammar for generating output from the internal
representation.  However, those generators require yet another set of
semantic actions to be written, transforming the internal representation
into an AST\@.

>>>>

Second,  applications often need to produce output in the same
format as their input---for example, applications might both
read and write files, or both receive and send network packets.
Most parser generators focus on just parsing an input, rather
than producing also an output, thus requiring the programmer to manually
construct outputs, which is work-intensive and more code that could contain errors.
Some parser generators, such as
Boost.Spirit~\cite{boost-spirit},
allow reusing the grammar for generating output from the internal
representation.  However, those generators require yet another set of
semantic actions to be written, transforming the internal representation
into an AST\@.

### 2014-05-02 paper/osdi14/motivation.tex
Fixed citations

Android application bundles are based on ZIP files, so we decided to conduct a systematic studies of
vulnerabilities related to ZIP parsing.  
The ZIP format has been associated with many vulnerabilities, and the
PROTOS Genome project~\cite{protoc-c10-archive} found numerous security vulnerabilities in most
implementations of ZIP and other archive formats that are directly
related to input handling. We extend this study by looking at the CVE database.

>>>>

Android application bundles are based on ZIP files, so we decided to conduct a systematic studies of
vulnerabilities related to ZIP parsing.  
The ZIP format has been associated with many vulnerabilities, and the
PROTOS Genome project~\cite{protos-c10-archive} found numerous security vulnerabilities in most
implementations of ZIP and other archive formats that are directly
related to input handling. We extend this study by looking at the CVE database.
